Hydras \& Co.

### 2022-03-14 doc/part-hydras.tex
corrections chapter 2

In order to describe trees where each node can have an arbitrary (but finite) number of sons, it is usual to define a type where each node carries a \emph{forest}, \emph{i.e} a list of trees
(see for instance Chapter 14, pages 400-406 of \cite{BC04,BC04ch14}).

@@

\subsubsection{Example}
Let us prove the transformation of \texttt{Hy'} into \texttt{Hy''} (see Fig.~\vref{fig:Hy3}). We use an experimental set of tactics for specifying the place where the 
interaction between Hercules and the hydra holds.

@@

Prove that, if $h$ is not a simple head, then there exists a unique $h'$ such that \texttt{h}  is transformed into \texttt{ h'} in one round, according to this restriction.

@@

\vspace{4pt}
\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Definitions.html}{Hydra.Hydra\_Definitions}}
\label{types:Battle}
\index{hydras}{Library Hydra!Type classes!Battle}

@@

\vspace{4pt}
\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Definitions.html\#free}{Hydra.Hydra\_Definitions}}

@@

\vspace{4pt}
\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Definitions.html\#standard}{Hydra.Hydra\_Definitions}}

\input{movies/snippets/Hydra_Definitions/standardDef}

@@

\vspace{4pt}
\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Definitions.html\#fight}{Hydra.Hydra\_Definitions}}

@@

\vspace{4pt}
\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Lemmas.html}{Hydra.Hydra\_Lemmas}}

\noindent
\input{movies/snippets/Hydra_Lemmas/battleTrans}

@@

\subsection{The beginning of hostilities}
During the two first rounds, our hydra loses its two rightmost heads.  Figure~\vref{fig:hinit-plus2} shows the state of the hydra   just before the third round.

@@

\subsection{Testing  \dots}
In order to study \emph{experimentally} the different  configurations of the  battle, we will use a simple data type for representing the states as tuples composed of
the round number, and the respective number of daughters  \texttt{h2}, \texttt{h1}, and heads
of the current hydra.

@@

Let us define a binary relation associated with every round of the battle.
In the following definition \texttt{i} is associated with the round number (or date, if we consider a discrete time), and \texttt{a}, \texttt{b}, \texttt{c} respectively associated with the number of \texttt{h2}, \texttt{h1} and heads connected to the hydra's foot.

@@

\begin{enumerate}
\item  Characterization of regularities of some events
\item Study of the beginning of the battle
\item Computing the exact length of the battle.
\end{enumerate}

@@

Let $B$ be an instance of class \texttt{Battle}. A \emph{variant} for $B$ consists
in a well-founded relation $<$  on some type \texttt{A}, and a function
(also called a \emph{measure}) \texttt{m:Hydra->A} such that for any successive steps $(i,h)$ and $(1+i,h')$  of a battle in $B$, the inequality $m(h')<m(h)$ holds.

@@

\inputsnippets{ON_Generic/ONDefsa, ON_Generic/ONDefsb}

>>>>

In order to describe trees where each node can have an arbitrary (but finite) number of sons, it is usual to define a type where each node carries a \emph{forest}, \emph{i.e} a list of trees
(see for instance Chapter 14, pages 400-406 of \cite{BC04}, also available as~\cite{BC04ch14}).

@@

\subsubsection{Example}
Let us prove the transformation of \texttt{Hy'} into \texttt{Hy''} (see Fig.~\vref{fig:Hy3}). We use an experimental set of tactics\footnote{See the \texttt{Ltac} definitions in~\href{../theories/html/hydras.Hydra.Hydra_Definitions.html\#R2}{Hydra.Hydra\_Definitions.}}  for specifying the place where the 
interaction between Hercules and the hydra holds.

@@

Prove that, if $h$ is not a simple head, then there exists a unique $h'$ such that $h$  is transformed into $h'$ in one round, according to this restriction.

@@

\vspace{6pt}
\noindent
\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Definitions.html}{Hydra.Hydra\_Definitions}}
\label{types:Battle}
\index{hydras}{Library Hydra!Type classes!Battle}

@@

\vspace{6pt}
\noindent
\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Definitions.html\#free}{Hydra.Hydra\_Definitions}}

@@

\vspace{6pt}
\noindent
\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Definitions.html\#standard}{Hydra.Hydra\_Definitions}}
\input{movies/snippets/Hydra_Definitions/standardDef}

@@

\vspace{6pt}
\noindent\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Definitions.html\#fight}{Hydra.Hydra\_Definitions}}

@@

\vspace{6pt}
\noindent\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Lemmas.html}{Hydra.Hydra\_Lemmas}}
\noindent
\input{movies/snippets/Hydra_Lemmas/battleTrans}

@@

\subsection{First rounds}
During the two first rounds, our hydra loses its two rightmost heads.  Figure~\vref{fig:hinit-plus2} shows the state of the hydra   just before the third round.

@@

\subsection{Testing  \dots}
\label{sect:testing}
In order to study \emph{experimentally} the different  configurations of the  battle, we will use a simple data type for representing the states as tuples composed of
the round number, and the respective number of daughters  \texttt{h2}, \texttt{h1}, and heads
of the current hydra.

@@

Let us define a binary relation associated with every round of the battle.
In the following definition \texttt{i} is associated with the round number (or date, if we consider a discrete time), and \texttt{a}, \texttt{b}, \texttt{c} respectively associated with the number of occurrences of \texttt{h2}, \texttt{h1} and heads connected to the hydra's foot.

@@

\begin{enumerate}
\item  Characterization and proofs of regularities of some events (inspired by our experiments of Sect.~\ref{sect:testing}).
\item Study of the beginning of the battle
\item Computing the exact length of the battle.
\end{enumerate}

@@

Let $B$ be an instance of class \texttt{Battle}. A \emph{variant} for $B$ consists
in a well-founded relation $<$  on some type \texttt{A}, and a function
(also called a \emph{measure}) $m:\texttt{Hydra}\rightarrow A$ such that for any successive steps $(i,h)$ and $(1+i,h')$  of a battle in $B$, the inequality $m(h')<m(h)$ holds.

@@

\inputsnippets{ON_Generic/ONDefsa}
\inputsnippets{ON_Generic/ONDefsb}
